Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-17 paper/paper.tex
Little formatting tweaks

We introduced the proportion of target vertices that are at least 3 apart as a
feature expecting it to be helpful in distinguishing between
\Glasgow variants---if few vertices are far apart, longer paths are unlikely to
be useful. However, in practice this feature also gives a rough indication of
how sparse the graph is---locally all-different filtering is weak and expensive
on dense graphs, and the feature turned out to be helpful for selecting between
\Glasgow and \LAD variants too.

@@

\begin{enumerate}
    \item If \IncompleteLAD removes at least \SI{28.014755}{\percent} of the pairs,
        and at least \SI{94.117645}{\percent} of the values from at least one domain,
        then pick \PathLAD.
    \item If the target has at least $610$ vertices, and if the maximum
        distance between any two pattern vertices is at most $8$, and if the
        pattern is not regular, and if the time taken to compute the
        distance-based features on the target graph is no more than
        \SI{1277}{\ms}, then pick \PathLAD.
    \item If \IncompleteLAD filtering removed at least \SI{5.904644}{\percent} of
        possible pairs, and if less than \SI{84.6565}{\percent} of the pattern
        vertices are within distance 2 of each other, then pick \PathLAD.
    \item Otherwise, pick \GlasgowTwo.
\end{enumerate}

>>>>

\noindent
We introduced the proportion of target vertices that are at least 3 apart as a
feature expecting it to be helpful in distinguishing between
\Glasgow variants---if few vertices are far apart, longer paths are unlikely to
be useful. However, in practice this feature also gives a rough indication of
how sparse the graph is---locally all-different filtering is weak and expensive
on dense graphs, and the feature turned out to be helpful for selecting between
\Glasgow and \LAD variants too.

@@

\begin{enumerate}
    \item If \IncompleteLAD presolving removes at least
        \SI{28.014755}{\percent} of the pairs, and at least
        \SI{94.117645}{\percent} of the values from at least one domain, then
        pick \PathLAD.
    \item If the target has at least $610$ vertices, and if the maximum
        distance between any two pattern vertices is at most $8$, and if the
        pattern is not regular, and if the time taken to compute the
        distance-based features on the target graph is no more than
        \SI{1277}{\ms}, then pick \PathLAD.
    \item If \IncompleteLAD filtering removed at least \SI{5.904644}{\percent} of
        possible pairs, and if less than \SI{84.6565}{\percent} of the pattern
        vertices are within distance 2 of each other, then pick \PathLAD.
    \item Otherwise, pick \GlasgowTwo.
\end{enumerate}
